### 2012-01-30 trunk/GUIErrorDetector/paper/abstract.tex
significant revise based on mike's comments

This paper presents a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph reachability problem with
thread spawning as the sources and GUI object accessing as the sinks. 
Heavy use of reflection in modern GUI applications makes existing
call graph construction algorithms fail to build a good
call graph. Thus, we present a method to overcome the limitations, and
build reflection-aware call graphs.

@@

We implemented our technique and instantiated it on four popular GUI
platforms: SWT, Eclipse plugin development framework, Java Swing, and
Android. In an evaluation on XX subjects over XXX LOC, our technique
found a number of real-world errors, suggesting its effectiveness
and showing good scalability.

>>>>

This paper presents a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph reachability problem with
thread spawning as the sources and GUI object accessing as the sinks. 
Existing call graph construction algorithms fail to build a good
call graph for modern GUI applications, because of heavy use of reflection.
Thus, we present a method to build reflection-aware call graphs.

@@

We implemented our technique and instantiated it for four popular GUI
platforms: SWT, the Eclipse plugin development framework, Swing, and
Android. In an evaluation on 9 programs comprising 67000 LOC, our technique
found both previously-known and unknown errors.

%a number of real-world errors, suggesting its effectiveness
%and showing good scalability.
